---
title: "Test-retest reliability model results for all parcels"
output: 
    html_document:
        toc: false
        toc_depth: 2
        toc_float: false
        number_sections: false
        df_print: paged
---

```{r, setup, include = FALSE}

knitr::opts_chunk$set(dpi = 300)

library(here)
library(tidyverse)
library(patchwork)

source(here("code", "_constants.R"))
source(here("code", "inferential", "_plotting.R"))
core32_roi <- rois[core32]

debugging <- FALSE
input_name <- "Schaefer400_stats.rds"
test_session <- "baseline"
responses <- c("uv", "rda")  # The first one is used as the base level
cont_networks <- c("ContA", "ContB", "DorsAttnA", "DorsAttnB")

dat <- readRDS(here("out", "inferential", atlas_nm, input_name))
dat <- bind_rows(dat, .id = "model__response__session") %>%
  separate(model__response__session, c("model", "response", "session"), sep = "__") %>%
  filter(session %in% .env$test_session) %>%
  select(-c(model, session)) %>%
  arrange(region, response)

# Note: The TRRs were calculated in `code/spatial/cmp_proj.R` from the spatial models
cor_res <- read_csv(here("out", "inferential", "pearson_correlations.csv")) %>%
  filter(subjects == "full", model == "wo_divnorm", response %in% .env$responses) %>%
  select(region, response, trr)

bayes_res <- dat %>%
  filter(Term == "TRR") %>%
  rename(trr = Estimate) %>%
  select(region, response, trr)

models <- c("Pearson", "Bayesian")
trr_res <- bind_rows(list(Pearson = cor_res, Bayesian = bayes_res), .id = "model") %>%
  mutate(
    response = factor(response, responses, ordered = T),
    model = factor(model, models, ordered = T),
    network = map_chr(region, ~ strsplit(., "_")[[1]][[3]]),
    network_roi = if_else(network %in% cont_networks, network, "others"),
    network_roi = na_if(network_roi, "others")
  ) %>%
  arrange(network_roi, region, model, response)
```

(New) contingency table:

```{r, contingency, echo = F, message = F}
crres <- cor_res %>% rename(ICC = trr)
trres <- dat %>%
  filter(Term == "TRR") %>%
  rename(HBM_MAP = Estimate, uncertainty = `Est.Error`) %>%
  select(region, response, HBM_MAP, uncertainty)

res <- inner_join(crres, trres) %>%
  pivot_wider(names_from = response, values_from = c(ICC, HBM_MAP, uncertainty))

head(res)
```

Highly reliable regions:

```{r, high-trr, echo = F, message = F}
trr_thres <- 0.7
for (mdl in models) {
  for (res in responses) {
    tmp <- trr_res %>%
      filter(response == .env$res, model == .env$mdl)
    n_reliable <- sum(tmp$trr > trr_thres)
    fig <- brain_plot(tmp, stat_term = "trr", lim = c(trr_thres, 1),
      fig_title = paste(mdl, res, ", n =", n_reliable))
    if (mdl == models[[1]] & res == responses[[1]]) figs <- fig else figs <- figs + fig
  }
}
figs <- figs + plot_layout(nrow = 2, guides = "collect") +
  plot_annotation(title = paste("Parcels with TRR >", trr_thres))
if (debugging) ggsave("tmp.png", plot = figs, width = 8, height = 4) else print(figs)
```

We take a look at the fixed effect:

```{r, scatters-t, echo = FALSE, message = FALSE, fig.dim = c(8, 4)}
lim <- c(0, 8)
for (i in c(1, 2)) {
  tmp <- dat %>%
    filter(Term == paste0("hilo_wave", i)) %>%
    mutate(
      t = abs(Estimate) / `Est.Error`,
      network = map_chr(region, ~ strsplit(., "_")[[1]][[3]]),
      is_ctrl_region = network %in% cont_networks
    ) %>%
    select(response, t, region, is_ctrl_region) %>%
    pivot_wider(values_from = t, names_from = response)
  fig <- ggplot(tmp) +
    aes(x = uv, y = rda, color = is_ctrl_region) +
    scale_color_manual(values = c("TRUE" = "red", "FALSE" = "#7e7e7e77")) +
    geom_point() +
    stat_ellipse() +
    geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
    labs(x = "uv", y = "rda", title = paste0("wave", i)) +
    xlim(lim[[1]], lim[[2]]) +
    ylim(lim[[1]], lim[[2]])
  if (i == 1) figs <- fig else figs <- figs + fig
}
figs <- figs +
  plot_annotation(title = "abs(t(hilo)) for each wave and response variable")
if (debugging) ggsave("tmp.png", plot = figs, width = 8, height = 4) else print(figs)
```

Here we plot the TRRs estimated by Pearson correlation and hierarchical Bayesian model (no_lscov_symm).

```{r, scatters-uvmv, echo = FALSE, message = FALSE, fig.dim = c(8, 4)}
lim <- range(trr_res$trr)
tmp <- trr_res %>%
  pivot_wider(values_from = trr, names_from = response)
for (mdl in models) {
  fig <- ggplot(tmp %>% filter(model == .env$mdl)) +
    aes(x = uv, y = rda, color = network_roi) +
    # scale_color_viridis_d(na.value = "#bebebe77") +
    scale_color_brewer(palette = "Set1", na.value = "#bebebe77") +
    geom_point() +
    geom_abline(intercept = 0, slope = 1) +
    geom_rug() +
    labs(x = "uv", y = "rda", title = mdl) +
    xlim(lim[[1]], lim[[2]]) +
    ylim(lim[[1]], lim[[2]])
  if (mdl == "Pearson") figs <- fig else figs <- figs + fig
}
figs <- figs + plot_layout(guides = "collect") +
  plot_annotation(title = paste("TRR over all regions estimated by different methods"))
if (debugging) ggsave("tmp.png", plot = figs, width = 8, height = 4) else print(figs)
```

We fit two ellipses for the distribution over control and non-control regions respectively.

```{r, fit-ellipses, echo = F, message = F, fig.dim = c(8, 4)}
# lim <- range(trr_res$trr)
lim <- c(-0.55, 1.25)
tmp <- trr_res %>%
  pivot_wider(values_from = trr, names_from = response) %>%
  mutate(is_ctrl_region = !is.na(network_roi))
for (mdl in models) {
  fig <- ggplot(tmp %>% filter(model == .env$mdl)) +
    aes(x = uv, y = rda, color = is_ctrl_region) +
    scale_color_manual(values = c("TRUE" = "red", "FALSE" = "#7e7e7e77")) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1) +
    stat_ellipse() +
    labs(x = "uv", y = "rda", title = mdl) +
    xlim(lim[[1]], lim[[2]]) +
    ylim(lim[[1]], lim[[2]])
  if (mdl == "Pearson") figs <- fig else figs <- figs + fig
}
figs <- figs + plot_layout(guides = "collect") +
  plot_annotation(title = paste("TRR over all regions estimated by different methods"))
if (debugging) ggsave("tmp.png", plot = figs, width = 8, height = 4) else print(figs)
```

Then we investigate the improvements by replacing Pearson correaltion with Bayesian model:

```{r, scatter-bias, echo = F, message = F, fig.dim = c(6, 6), out.width = "50%", fig.align="center"}
tmp <- get_diff_dat(trr_res, "model", val_term = "trr") %>%
  pivot_wider(values_from = trr, names_from = response)
lim2 <- range(tmp[c("uv", "rda")])
fig <- ggplot(tmp) +
  aes(x = uv, y = rda, color = network_roi) +
  scale_color_brewer(palette = "Set1", na.value = "#bebebe77") +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_rug() +
  labs(x = "uv_HBM - uv_Pearson", y = "rda_HBM - rda_Pearson",
    title = "Difference between the TRRs estimated by different models") +
  xlim(lim2[[1]], lim2[[2]]) +
  ylim(lim2[[1]], lim2[[2]])
if (debugging) ggsave("tmp.png", plot = fig) else print(fig)
```

We seperate this plot for each network to investiagte which network benefits most from hierarchical Bayesian modeling:

```{r, scatters-bias, echo = F, message = F, fig.dim = c(16, 9)}
tmp <- get_diff_dat(trr_res, "model", val_term = "trr") %>%
  pivot_wider(values_from = trr, names_from = response)
lim2 <- range(tmp[c("uv", "rda")])
networks <- unique(tmp$network)
for (i in seq_along(networks)) {
  palet <- c("red")
  names(palet) <- networks[[i]]
  fig <- ggplot(tmp) +
    aes(x = uv, y = rda, color = network) +
    scale_color_manual(values = palet, na.value = "#bebebe26") +
    geom_point() +
    geom_abline(intercept = 0, slope = 1) +
    geom_vline(xintercept = 0, linetype = "dotted") +
    geom_hline(yintercept = 0, linetype = "dotted") +
    labs(x = "uv", y = "rda",
      title = networks[[i]]) +
    xlim(lim2[[1]], lim2[[2]]) +
    ylim(lim2[[1]], lim2[[2]]) +
    theme(legend.position = "none")
  if (i == 1) figs <- fig else figs <- figs + fig
}
figs <- figs +
  plot_annotation(title = "TRR(HBM) - TRR(Pearson) for different response variables")
if (debugging) ggsave("tmp.png", plot = figs, width = 16, height = 9) else print(figs)
```

We then take a look at whether the improvement by HBM correlates with Pearson(TRR).

```{r, scatter-trr-bias, echo = F, message = F, fig.dim = c(8, 4)}
tmp <- trr_res %>%
  pivot_wider(values_from = trr, names_from = model) %>%
  mutate(Diff = Bayesian - Pearson)
lim1 <- range(trr_res$trr)
lim2 <- range(tmp$Diff)
for (res in responses) {
  fig <- ggplot(tmp %>% filter(response == .env$res)) +
    aes(x = Pearson, y = Diff, color = network_roi) +
    scale_color_brewer(palette = "Set1", na.value = "#bebebe77") +
    geom_point() +
    # geom_smooth(method = "lm") +
    labs(x = "Pearson", y = "Difference", title = res) +
    xlim(lim1[[1]], lim1[[2]]) +
    ylim(lim2[[1]], lim2[[2]])
  if (res == "uv") figs <- fig else figs <- figs + fig
}
figs <- figs + plot_layout(guides = "collect") +
  plot_annotation(title = "Pearson(TRR) over HBM(TRR) - Pearson(TRR) for each response")
if (debugging) ggsave("tmp.png", plot = figs, width = 8, height = 4) else print(figs)
```

Then we plot the difference between multivariate and univariate methods for each TRR model (Pearson correlation or HBM):

```{r, scatter-uvmv-diff, echo = F, message = F, fig.dim = c(6, 6), out.width = "50%", fig.align="center"}
tmp <- get_diff_dat(trr_res, "response", val_term = "trr") %>%
  pivot_wider(values_from = trr, names_from = model)
lim2 <- range(tmp[c("Pearson", "Bayesian")])
fig <- ggplot(tmp) +
  aes(x = Pearson, y = Bayesian, color = network_roi) +
  # scale_color_viridis_d(na.value = "#bebebe77") +
  scale_color_brewer(palette = "Set1", na.value = "#bebebe77") +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_rug() +
  labs(x = "rda_Pearson - uv_Pearson", y = "rda_HBM - uv_HBM",
    title = "Difference between the TRRs estimated by different response variables") +
  xlim(lim2[[1]], lim2[[2]]) +
  ylim(lim2[[1]], lim2[[2]])
if (debugging) ggsave("tmp.png", plot = fig) else print(fig)
```

We seperate this plot for each network to investiagte which network benefits most from multivariate methods:

```{r, scatters-uvmv-diff, echo = F, message = F, fig.dim = c(16, 9)}
tmp <- get_diff_dat(trr_res, "response", val_term = "trr") %>%
  pivot_wider(values_from = trr, names_from = model)
lim2 <- range(tmp[c("Pearson", "Bayesian")])
networks <- unique(tmp$network)
for (i in seq_along(networks)) {
  palet <- c("red")
  names(palet) <- networks[[i]]
  fig <- ggplot(tmp) +
    aes(x = Pearson, y = Bayesian, color = network) +
    scale_color_manual(values = palet, na.value = "#bebebe26") +
    geom_point() +
    geom_abline(intercept = 0, slope = 1) +
    geom_vline(xintercept = 0, linetype = "dotted") +
    geom_hline(yintercept = 0, linetype = "dotted") +
    labs(x = "Pearson", y = "Bayesian",
      title = networks[[i]]) +
    xlim(lim2[[1]], lim2[[2]]) +
    ylim(lim2[[1]], lim2[[2]]) +
    theme(legend.position = "none")
  if (i == 1) figs <- fig else figs <- figs + fig
}
figs <- figs +
  plot_annotation(title = "TRR(rda) - TRR(uv) estimated by different methods")
if (debugging) ggsave("tmp.png", plot = figs, width = 16, height = 9) else print(figs)
```