---
title: "Test-retest reliability model results"
output: 
    html_document:
        toc: false
        toc_depth: 2
        toc_float: false
        number_sections: false
        df_print: paged
---

```{r, setup, include = FALSE}
library(here)
library(tidyverse)
library(patchwork)

source(here("code", "_constants.R"))
source(here("code", "inferential", "_plotting.R"))
core32_roi <- rois[core32]

debugging <- F
input_name <- "core32_stats.rds"
test_session <- "baseline"
responses <- c("uv", "rda", "ridge")  # The first one is used as the base level
models <- c("full", "no_lscov", "no_lscov_symm", "fixed_sigma")

dat <- readRDS(here("out", "inferential", atlas_nm, input_name))
dat <- bind_rows(dat, .id = "model__response__session") %>%
  separate(model__response__session, c("model", "response", "session"), sep = "__") %>%
  filter(session %in% .env$test_session) %>%
  mutate(model = factor(model, .env$models, ordered = T),
    response = factor(response, .env$responses, ordered = T)) %>%
  arrange(model, response, region)

```

# Relilability Modeling Results

This document outlines the test-retest reliability (TRR) models considered in this project, and relavant results. The TRRs are calculated in "baseline" session only.

## Design and Notation


- trial $t \in 1, ..., T$
- condition $c \in \{\text{incongruent}, \text{congruent}\}$
- task $k \in \{\text{axcpt}, \text{stroop}\}$
- session $s \in \{\text{baseline}, \text{proactive}, \text{reactive}\}$
- repetition $r \in \{\text{test}, \text{retest}\}$
- participant $p \in 1, ..., P$
- Response variable: $y$, considered here for a single ROI and for a single type of spatial model (i.e., univariate or multivariate model)

The following indicator variables will be used to denote a $\textbf{dummy or treatment-coding}$ scheme:

$$
\begin{equation*}
\begin{split}
	&\text{incon} = 
	\begin{cases}
		1 & \text{if condition = incongruent} \\
		0 & \text{if condition = congruent}
	\end{cases},\\
	&\text{retest} = 
	\begin{cases}
		1 & \text{if repetition = retest} \\
		0 & \text{if repetition = test}
	\end{cases},\\
	&\text{test} = 1 - \text{retest}
\end{split}
\end{equation*}
$$


The following expression will be used to denote a $\textbf{contrast-coding}$ scheme for the condition factor:

$$
  \text{stroop} = 
  \begin{cases}
    \frac{1}{2} & \text{if condition = incongruent} \\
    -\frac{1}{2} & \text{if condition = congruent}
  \end{cases}
$$

## Model 0: Pearson correlations

$$
z_{rp} = {\langle y_{tcrp} \rangle}_{t,\ c = \text{Incongruent}} - {\langle y_{tcrp} \rangle}_{t,\ c = \text{Congruent}} \\
\text{TRR} = \text{Cor}(z_{1p}, z_{2p})
$$

First we plot the TRR estimated from univariate or multivariate methods for each region:

```{r, Pearson-scatter, echo = FALSE, warning = FALSE, message = FALSE, fig.dim = c(8, 6)}

# Input data
# Note: The TRRs were calculated in `code/spatial/cmp_proj.R` from the spatial models
# (see `fnames`) and then saved down manually.
cor_res <- read_csv(here("out", "inferential", "pearson_correlations.csv")) %>%
  filter(subjects == "full", model == "wo_divnorm", response %in% c("ridge", "uv")) %>%
  # mutate(response = if_else(response == "ridge", "mv", response)) %>%
  select(region, response, trr) %>%
  pivot_wider(names_from = response, values_from = trr) %>%
  mutate(is_core32 = region %in% .env$core32_roi)
print("TRRs estimated from Pearson correlation:")
cor_res

lim <- range(cor_res[, c("ridge", "uv")])
fig <- ggplot(cor_res) +
  aes(x = uv, y = ridge, color = is_core32) +
  scale_color_manual(values = c("black", "red")) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1) +
  geom_rug() +
  labs(x = "uv", y = "ridge",
    title = "TRR estimated by Pearson correlation over all regions") +
  xlim(lim[[1]], lim[[2]]) +
  ylim(lim[[1]], lim[[2]])
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

And the distribution of the difference between the result of "ridge" and "uv":

```{r, Pearson-diff, echo = FALSE, fig.dim = c(8, 6)}
cor_res <- cor_res %>% mutate(`ridge - uv` = ridge - uv)
mdiff <- cor_res %>% group_by(is_core32) %>% summarize(diff = mean(`ridge - uv`))
fig <- ggplot(cor_res) +
  aes(x = `ridge - uv`, color = is_core32) +
  geom_density() +
  # geom_vline(xintercept = mdiff, linetype = "dashed") +
  # annotate("text", label = "mean", x = mdiff, y = 1) +
  labs(x = "ridge - uv", y = "density", title = "Distribution of the difference in TRRs")
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

## Model 1: “fixed_sigma"

This model is t-distributed, where the sigma term is independent from the conditions:

```{r, eval = FALSE}
formula_string <-
  paste0(
    " ~ ",
    "0 + mean_wave1 + mean_wave2 + hilo_wave1 + hilo_wave2 + ",
    "(0 + mean_wave1 + mean_wave2 | subj) + (0 + hilo_wave1 + hilo_wave2 | subj)"
  )
formula_sigma <- formula(sigma ~ 1)
```

We made the same plots, but this time we only include core32 regions (same below).

```{r, fixed-sigma-scatter, echo = FALSE, fig.dim = c(8, 6)}

# Input data
fs_new <- dat %>%
  filter(Term == "TRR", model == "fixed_sigma", response %in% c("ridge", "uv")) %>%
  select(response, Estimate, region) %>%
  pivot_wider(names_from = response, values_from = Estimate)
print("TRRs estimated from 'fixed_sigma' model:")
fs_new

lim <- range(fs_new[, c("ridge", "uv")])
fig <- ggplot(fs_new) +
  aes(x = uv, y = ridge) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1) +
  geom_rug() +
  labs(x = "uv", y = "ridge",
    title = "TRR estimated by 'fixed_sigma' model over core32 regions") +
  xlim(lim[[1]], lim[[2]]) +
  ylim(lim[[1]], lim[[2]])
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

Here we compare the results when we either normalize the data before calculating the response or not.

```{r, w-wo-divnorm-fs, echo = FALSE, fig.dim = c(8, 6)}
fs_old <- readRDS(here("out", "inferential", "wo_divnorm", "core32_stats.rds"))
fs_old <- bind_rows(fs_old, .id = "model__response__session") %>%
  separate(model__response__session, c("model", "response", "session"), sep = "__") %>%
  filter(Term == "TRR") %>%
  select(response, region, Estimate) %>%
  pivot_wider(names_from = response, values_from = Estimate)
fs_all <- bind_rows(list(wo = fs_old, w = fs_new), .id = "prep") %>%
  pivot_wider(names_from = prep, values_from = c(ridge, uv))
fs_diff <- fs_all %>%
  mutate(ridge_diff = ridge_w - ridge_wo, uv_diff = uv_w - uv_wo)

lim <- range(fs_diff[, c("ridge_diff", "uv_diff")])
fig <- ggplot(fs_diff) +
  aes(x = uv_diff, y = ridge_diff) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1) +
  geom_abline(intercept = 0, slope = -1, linetype = "dotted") +
  geom_rug() +
  labs(x = "uv_divnorm - uv_no_divnorm", y = "ridge_divnorm - ridge_no_divnorm",
    title = "TRR difference with or without divisive normalization") +
  xlim(lim[[1]], lim[[2]]) +
  ylim(lim[[1]], lim[[2]])
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

We can see that divisive normalization seems to reduce TRR for "uv" but did not make big difference for "ridge". Therefore, divisive normalization (that we used here and after) might be biased towards multivariate methods without improving the overall result. Here we count the best response variable ("uv" or "ridge", with or without divnorm) over 32 regions:

```{r, fs-best, echo = FALSE}
fs_all$best_res <- apply(fs_all, 1, function(r) names(r)[[which.max(r[2:5]) + 1]])
fig <- ggplot(fs_all) +
  aes(x = best_res) +
  geom_bar() +
  labs(title = "Counts of the best response variable over core32 parcels")
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

## Model 2: "no_lscov_symm"

This model is similar to model 1 but the sigma term is no longer independent from the conditions. Instead, it is also predicted with a same formula as that for the mean:

```{r, eval = FALSE}
formula_string <-
  paste0(
    " ~ ",
    "0 + mean_wave1 + mean_wave2 + hilo_wave1 + hilo_wave2 + ",
    "(0 + mean_wave1 + mean_wave2 | subj) + (0 + hilo_wave1 + hilo_wave2 | subj)"
  )
formula_sigma <-
  formula(
    sigma ~ 0 + mean_wave1 + mean_wave2 + hilo_wave1 + hilo_wave2 +
    (0 + mean_wave1 + mean_wave2 | subj) + (0 + hilo_wave1 + hilo_wave2 | subj)
  )
```

The same scatter plot:

```{r, no-lscov-symm-scatter, echo = FALSE, fig.dim = c(8, 6)}

# Input data
nls_dat <- dat %>%
  filter(Term == "TRR", model == "no_lscov_symm", response %in% c("ridge", "uv")) %>%
  select(response, Estimate, region) %>%
  pivot_wider(names_from = response, values_from = Estimate)
print("TRRs estimated from 'no_lscov_symm' model:")
nls_dat

lim <- range(nls_dat[, c("ridge", "uv")])
fig <- ggplot(nls_dat) +
  aes(x = uv, y = ridge) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1) +
  geom_rug() +
  labs(x = "uv", y = "ridge",
    title = "TRR estimated by 'no_lscov_symm' model over core32 regions") +
  xlim(lim[[1]], lim[[2]]) +
  ylim(lim[[1]], lim[[2]])
if (debugging) ggsave("tmp.png", plot = fig, width = 8, height = 6) else fig
```

Violin plot:

```{r, no-ls-cov-symm-violin, echo = FALSE}
tmp <- nls_dat %>%
  pivot_longer(values_to = "TRR", names_to = "response", cols = c(ridge, uv))
fig <- ggplot(tmp) +
  aes(x = response, y = TRR, color = response) +
  geom_violin(draw_quantiles = c(0.25, 0.50, 0.75)) +
  geom_jitter(size = 0.2, height = 0, width = 0.1) +
  labs(x = "response", y = "TRR", title = "Distribution of TRR")
if (debugging) ggsave("tmp.png", plot = fig) else fig
```

## Comparison

```{r, comparison, echo = FALSE, fig.dim = c(16, 9)}
tmp1 <- cor_res %>%
  filter(is_core32 == TRUE) %>%
  select(region, ridge, uv) %>%
  mutate(model = "Pearson")
tmp2 <- dat %>%
  filter(Term == "TRR", response %in% c("ridge", "uv")) %>%
  select(model, response, Estimate, region) %>%
  pivot_wider(values_from = Estimate, names_from = response)
responses <- c("Pearson", "fixed_sigma", "no_lscov_symm", "no_lscov", "full")
all_trr <- bind_rows(tmp1, tmp2) %>%
  mutate(model = factor(model, ordered = TRUE, levels = .env$responses))

lim <- range(all_trr[, c("ridge", "uv")])
figs <- NULL
for (res in responses) {
  tmp <- all_trr %>% filter(model == .env$res)
  fig <- ggplot(tmp) +
    aes(x = uv, y = ridge) +
    geom_point(alpha = 0.5) +
    geom_abline(intercept = 0, slope = 1) +
    geom_rug() +
    labs(x = "uv", y = "ridge",
      title = res) +
    xlim(lim[[1]], lim[[2]]) +
    ylim(lim[[1]], lim[[2]])
  if (is.null(figs)) figs <- fig else figs <- figs + fig
}
figs + plot_layout(nrow = 2) +
  plot_annotation(title = "TRR from different models for different response variables")
if (debugging) ggsave("tmp.png", plot = figs, width = 16, height = 9) else figs
```