---
title: "Test-retest reliability models"
output: 
    html_document:
        toc: false
        toc_depth: 2
        toc_float: false
        number_sections: false
        df_print: paged
---

This document outlines the test-retest reliability models considered in this project.



```{r setup, results = FALSE, message = FALSE, echo = FALSE, warning = FALSE}

library(ggplot2)
library(reshape2)
library(magrittr)
library(colorspace)
library(knitr)
library(brms)

```


# Design and Notation


- trial $t \in 1, ..., T$
- condition $c \in \{\text{incongruent}, \text{congruent}\}$
- repetition $r \in \{\text{test}, \text{retest}\}$
- participant $p \in 1, ..., P$
- Response variable: $y$, considered here for a single ROI and for a single type of spatial model (i.e., univariate or multivariate model)


# The `full` model

- condition and repetition factors parameterized under "flat" (aka "no-intercept dummy") scheme


$$
\begin{equation}
	\label{eq:full}
	\begin{split}
		& y_{tcrp} \sim \mathcal{T}(\alpha_{crp}, \nu_{crp}) \\
		& \alpha_{crp} = m_{cr} + \mu_{crp} \\
		& \text{log } \nu_{crp} = \gamma_{cr} + \tau_{crp} \\
		& (\boldsymbol{\mu}_{p}, \boldsymbol{\tau}_{p})^{\intercal} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma})\\
		& \boldsymbol{\Sigma} = 
		\begin{bmatrix}
			\Sigma_{11} & \dots  & \Sigma_{18}\\
			\vdots & \ddots & \vdots\\
			\Sigma_{81} & \dots  & \Sigma_{88} 
		\end{bmatrix} \\
	\end{split}
\end{equation}
$$


```{r, eval = FALSE}
brms(
  y ~ 
    0 + congr_test + congr_retest + incon_test + incon_retest + 
    (0 + congr_test + congr_retest + incon_test + incon_retest | a | subj),
  sigma = 
    0 + congr_test + congr_retest + incon_test + incon_retest +
    (0 + congr_test + congr_retest + incon_test + incon_retest | a | subj)
)
```



# `no_lscov`

same form as `full`, except:

- independent location and scale


$$
\begin{equation}
	\label{eq:no_lscov}
	\begin{split}
		& y_{tcrp} \sim \mathcal{T}(\alpha_{crp}, \nu_{crp}) \\
		& \alpha_{crp} = m_{cr} + \mu_{crp} \\
		& \text{log } \nu_{crp} = \gamma_{cr} + \tau_{crp} \\
		& \boldsymbol{\mu}_{p} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma}_{l=\text{locat}}) \\
		& \boldsymbol{\tau}_{p} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma}_{l=\text{scale}}) \\
		& \boldsymbol{\Sigma}_{l} = 
			\begin{bmatrix}
				\Sigma_{11} & \dots  & \Sigma_{14}\\
				\vdots & \ddots & \vdots\\
				\Sigma_{41} & \dots  & \Sigma_{44} 
			\end{bmatrix}_{l} \\
	& \text{for } l \in \{\text{locat}, \text{scale}\}
	\end{split}
\end{equation}
$$


```{r, eval = FALSE}
brms(
  y ~ 
    0 + congr_test + congr_retest + incon_test + incon_retest + 
    (0 + congr_test + congr_retest + incon_test + incon_retest | subj),
  sigma ~
    0 + congr_test + congr_retest + incon_test + incon_retest +
    (0 + congr_test + congr_retest + incon_test + incon_retest | subj)
)
```



# `no_lscov_symm`

same form as `full`, except:

- independent location and scale
- paramaterized the condition factor $c$ using a contrast coding scheme, indexed by $c'$
- symmetric covariance structure


$$
\begin{equation}
	\label{eq:no_lscov_symm}
	\begin{split}
		& y_{tc'rp} \sim \mathcal{T}(\alpha_{c'rp}, \nu_{c'rp}) \\
		& \alpha_{c'rp} = m_{c'r} + \mu_{c'rp} \\
		& \text{log } \nu_{c'rp} = \gamma_{c'r} + \tau_{c'rp} \\
		& \boldsymbol{\mu}_{c'p} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma}_{(l=\text{locat})c'}) \\
		& \boldsymbol{\tau}_{c'p} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma}_{(l=\text{scale})c'}) \\
		& \boldsymbol{\Sigma}_{lc'} = 
		\begin{bmatrix}
			\Sigma_{11} & \Sigma_{12}\\
			\Sigma_{21} & \Sigma_{22} 
		\end{bmatrix}_{lc'} \\
		& \text{for } l \in \{\text{locat}, \text{scale}\}
	\end{split}
\end{equation}
$$


```{r, eval = FALSE}
brms(
  y ~ 
    0 + mean_test + mean_retest + stroop_test + stroop_retest + 
    (0 + mean_test + mean_retest | subj) +
    (0 + stroop_test + stroop_retest | subj),
  sigma ~
    0 + mean_test + mean_retest + stroop_test + stroop_retest +
    (0 + mean_test + mean_retest | subj) + 
    (0 + stroop_test + stroop_retest | subj)
)
```


# `fixed_sigma`

same form as full, except:

- independent location and scale
- paramaterized the condition factor $c$ using a contrast coding scheme, indexed by $c'$
- symmetric covariance structure
- a single $\nu$ (fixed scale)


$$
\begin{equation}
	\label{eq:fixed_sigma}
	\begin{split}
		& y_{tc'rp} \sim \mathcal{T}(\alpha_{c'rp}, \nu) \\
		& \alpha_{c'rp} = m_{c'r} + \mu_{c'rp} \\
		& \boldsymbol{\mu}_{c'p} \sim \mathcal{N}(\mathbf{0}, \boldsymbol{\Sigma}_{c'}) \\
		& \boldsymbol{\Sigma}_{c'} = 
		\begin{bmatrix}
			\Sigma_{11} & \Sigma_{12}\\
			\Sigma_{21} & \Sigma_{22} 
		\end{bmatrix}_{c'}
	\end{split}
\end{equation}
$$


```{r, eval = FALSE}
brms(
  y ~ 
    0 + mean_test + mean_retest + stroop_test + stroop_retest + 
    (0 + mean_test + mean_retest | subj) +
    (0 + stroop_test + stroop_retest | subj),
  sigma ~ 1
)
```

